Paper Report "MacroBase: Prioritizing Attention in Fast Data" \\ Big Data Storage and Processing Infrastructures

### 2019-03-20 paper-report.tex
sol

	\begin{flushleft}

@@

	\end{flushleft}

@@

		\\\textbf{2. Feature Transformation.} \textit{MacroBase} executes data transformations over the stream. These transformations can be statistical, datatype specific or time series specific operations. This feature placed at the beginning of the pipeline lets users to prepare or encode their data for the following steps without modifying later stages. Also given that the base type is unchanged in this feature (from data point to data point), it can be chained several times to apply different transformations.

@@

		\\\textbf{2. Basic Explanation Strategy} As the paper states, the first solution to apply risk ratio for several attribute sets is to search twice but this is a waste of time and effort. To solve this, MDP exploits the cardinality imbalance that reduces the attributes to explore and also takes advantage of individual item ratios computing them first as these are cheap or inexpensive and then the combinations. The final strategy is as follows: MDP calculates the attribute values with minimum risk ratio, then computes the supported outlier attribute combinations and finally computes the risk ratio for each combination based on their support in the inliers.

@@

	\begin{flushleft}

	\end{flushleft}
\end{document}

>>>>

@@

@@

		\\\textbf{2. Feature Transformation.} \textit{MacroBase} executes data transformations over the stream. These transformations can be statistical, datatype specific or time series specific operations. This feature placed at the beginning of the pipeline lets users to prepare or encode their data for the following steps without modifying later stages. Also given that the base type is unchanged in this feature (\textit{Point}$\rightarrow$\textit{Point}), it can be chained several times to apply different transformations.

@@

		\\\textbf{2. Basic Explanation Strategy.} As the paper states, the first solution to apply risk ratio for several attribute sets is to search twice but this is a waste of time and effort. To solve this, MDP exploits the cardinality imbalance that reduces the attributes to explore and also takes advantage of individual item ratios computing them first as these are cheap or inexpensive and then the combinations. The final strategy is as follows: MDP calculates the attribute values with minimum risk ratio, then computes the supported outlier attribute combinations and finally computes the risk ratio for each combination based on their support in the inliers.

@@

		To sum up and as we have seen in the paper, \textit{MacroBase} is an analytics engine that prioritizes attention in fast data streams. To achieve this, they focused the solution development in providing a flexible architecture that combines streaming classification and data explanation. This focus provided \textit{MacroBase} an increase in performance and result quality which have been useful in some environments that have been shown in the paper.
		\\In my opinion, I find the solution exposed in the paper pretty interesting. We have seen in IBD class solutions to analyse data and create monitoring pipelines, such as \textit{Apache Spark}, \textit{Apache Flink}, \textit{Apache Beam} etc. but all of these solutions had the same problem: after passing the data through the pipelines, there is still a human analysis of the resulting data to know where to focus attention. With \textit{MacroBase} this bottleneck can be avoided and we can get accurate conclusions over data way faster. The design approach done with \textit{MacroBase} makes it unique in the market, if the users want to get anything close to this solution, they must implement them themselves with other monitoring pipelines technologies like the ones mentioned above, with the handicap that these were not designed with the same focus, thus they will not be as accurate and fast as \textit{MacroBase}.
		\\I personally find the paper quality really good. They explained in depth the design of the solution with the detailed explanation about the choices they made when implementing it. They also explained the tests to prove the improvement in performance and accuracy and they explained the tools and steps done to verify them. The only negative point I can say about the paper/solution is that they do not talk how to deal with scalability in the main sections. Even with the high performance results achieved, \textit{MacroBase} should also support parallelization to deal with the still increasing data loads. This concern is mentioned in Appendix D, and they even tested parallelization with \textit{MacroBase}, obtaining less accurate results. However, they mentioned in this appendix that is at the moment subject of ongoing work, meaning that this concern is identified and there may be a solution in the near future. 
\end{document}
